---
title: "Basic example: model set-up"
author: "Nathan Green"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Introduction

This is a basic example of how to use the LTBI screening model. Other vignettes will show how to automate some of the running over multiple scenarios, and how to visualised the output.


## Fixed model parameters

Don't assume that everyone who enters the country doesn't leave.
```r
force_everyone_stays <- FALSE
```

Do we include the QALY loss of individuals who leave EWNI but then progress to active TB? If yes then we follow them to death rather than time of exit.
```r
ENDPOINT_QALY <- "death"
```

Rather than offer screening to _everyone_ immediately on entry, assume that we screen at random 0-5 years from entry.
```r
screen_with_delay <- TRUE
MAX_SCREEN_DELAY <- 5
```

Time horizon for active TB progression
```r
FUP_MAX_YEAR <- 100
```

```r
screen_age_range <- 18:45
```

We pick a single year cohort to simulate from. 2012 is the most recent complete year but we'll use the largest.
```r
year_cohort <- '2009'
```

## Scenario parameter values

We'll show later how to simulate over multiple scenarios but here we'll take the simplest case of a single scenario.
The scenario values are given in a _long_ format tibble such as the following.

```{r}
data("scenario_parameters", package = "LTBIscreeningproject")
scenario_parameters[[1]]
```


* `node` are the names of the nodes on the decision tree i.e. the steps along the screening, diagnosis and treatment pathway.
* `distn`, `min`, `max` specify the distibutions for whichever parameter is indicated.
* `scenario` in this case is superfluous.
* `val_type` indicates the paramter type i.e. is it cost or some health indicator. (__`QALYloss` is not a good name! Need to change__. This should really be `p` and we have another label for health.)
* `p` is the probability. If we rename the val_types then we can get rid of this column.


## Study data

Read-in the cleaned individual-level study. This is in accordance with the fixed model parameters above.

```r
data("sample_cleaned")
```

Data cleaning removes some entries and we also create new fields from the existing ones which we'll need later on.

* Remove duplicate pre-entry screened
* Remove duplicate notification dates
* Remove death before entry to UK
* Eligible screening age range only
* Create LTBI probabilities by WHO active TB group
    + Match active TB prevalence groups in dataset to previous study
    + Pareek M et al. Lancet Infect Dis. Elsevier Ltd; 2011;11(6)
* Create time-to-events, from UK entry to event dates
* Create UK entry to follow-up days
* Remove individual follow-up date before entry
* Remove TB before entry


## Cost-effectiveness parameter values

The data objects are created in the following script.
```r
source("scripts/01b-data-prep_cost-effectiveness.R", echo = TRUE)
```

The data are created with the date of the original and the discounted or inflated date as well as the reference from where it came.

Where available the parameter values are given as distibutions and their hyper-parameters.

This includes:

```{r}
data("cost_effectivness_params", package = "LTBIscreeningproject")

cfr_age_lookup
```

```{r}
unit_cost
```

```{r}
utility
```

```{r}
QALYloss
```

```{r}
NUM_SECONDARY_INF
```

