---
title: "Basic output plots"
author: "Nathan Green"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
  editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Introduction

We combine the cost and health results from the screening, testing and treatment decision tree with the cost and health results from the population model follow-up to defined end-point.
We then plot some basic cost-effectiveness planes.

Load packages

```{r, warning=F, message=F}
library(treeSimR)
library(LTBIscreeningproject)
library(dplyr)
library(data.tree)
library(purrr)
library(tibble)
library(magrittr)
library(plotCostEffectiveness)
library(ggplot2)
library(BCEA)
```

Load in data

```{r}
data("scenario_parameters", package = "LTBIscreeningproject")
load("aTB_CE_stats.RData")

dectree_res <- readRDS("decision_tree_output.Rds")
cohort <- readRDS("cohort.Rds")
```


## Create input matrices

We're going to use the `BCEA` package to calculate some additional values and do some of the plotting.
In order to use this we need to rearrange some of our data.

```{r}
# discount due to delay to screening
##TODO: what is actual number?
screen_discount <- 0.9

scenario.names <-
  c(0, seq_len(length(dectree_res))) %>%
  as.character(.)
```

Cost and QALY gain due to active TB in the population

```{r}
tb_cost <-
  aTB_CE_stats$cost_incur_person %>%
  do.call(cbind.data.frame, .) %>%
  add_column('0' = 0, .before = 1) %>%
  set_names(nm = scenario.names)

tb_QALYgain <-
  aTB_CE_stats$QALYgain_person %>%
  do.call(cbind.data.frame, .) %>%
  add_column('0' = 0, .before = 1) %>%
  set_names(nm = scenario.names)
```

Cost and QALY gain due to screening

```{r}
LTBI_cost <-
  purrr::map(dectree_res, "mc_cost") %>% 
  do.call(cbind.data.frame, .) %>%
  multiply_by(screen_discount) %>% 
  add_column('0' = 0, .before = 1)

LTBI_QALYgain <- 
  purrr::map(dectree_res, "mc_health") %>% 
  do.call(cbind.data.frame, .) %>%
  multiply_by(-screen_discount) %>% 
  add_column('0' = 0, .before = 1)

c.total <- as.matrix(LTBI_cost + tb_cost)
e.total <- as.matrix(LTBI_QALYgain + tb_QALYgain)

c.total
e.total
```


## Cost-effectiveness planes

```{r fig.width=5, fig.height=5}
screen.bcea <- BCEA::bcea(e = -e.total,  # Q1 - Q0 different way round in function!
                          c =  -c.total,
                          ref = 1,
                          interventions = colnames(e.total))

cbPalette <- colorRampPalette(c("red", "orange", "green", "blue"))(screen.bcea$n.comparisons)

gg <- contour2(screen.bcea, graph = "ggplot2", wtp = 20000)
gg + scale_colour_manual(values = cbPalette)

my_contour2(screen.bcea,
            graph = "ggplot2",
            wtp = 20000,
            CONTOUR_PC = "50%") +
  ggtitle('50th percentile contours') +
  scale_colour_manual(values = cbPalette)
```

