---
title: "Cost-effectiveness calculation"
author: "Nathan Green"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Introduction

This document demonstrates how we calculate the cost and QALY statistics.


## Analysis preparation

Load packages

```{r, warning=F, message=F}
library(treeSimR)
library(LTBIscreeningproject)
library(dplyr)
library(data.tree)
library(purrr)
```

We first need to read-in the decision tree output data and the individual cohort data.

```{r load-data}
dectree_res <- readRDS("decision_tree_output.Rds")
cohort <- readRDS("cohort.Rds")
```

```{r}
# data("cost_effectivness_params", package = "LTBIscreeningproject")
```

It is sometimes arkward to use the decision tree output in the format with the scenario number as the top level.
It may be more useful to have each output type at the top level, so we _transpose_ the data.

From

```{r}
lapply(dectree_res, FUN = function(x) lapply(x, head))
```

to

```{r}
# convert from scenario-wise to parameter-wise format
scenario_res <-
  dectree_res %>%
  purrr::transpose()

lapply(scenario_res, function(x) lapply(x, head))
```


We need to extract some specific values and initialise the variables for the cost-effectiveness statistics.

```{r}
n.scenarios <- length(dectree_res)

n.diseasefree.all_tb <-
  scenario_res$n_tb_screen_all %>%
  purrr::map(function(x) dplyr::filter(x, status == "disease-free")) %>%
  map(function(x) x$n)

n.diseasefree.uk_tb  <-
  scenario_res$n_tb_screen_uk %>%
  purrr::map(function(x) dplyr::filter(x, status == "disease-free")) %>%
  map(function(x) x$n)

n_uk_tb <- dectree_res$`1`$call$n.uk_tb
n_exit_tb <- dectree_res$`1`$call$n.exit_tb
n_all_tb <- n_exit_tb + n_uk_tb

N.mc <- dectree_res$`1`$call$N.mc

interv_cost <- vector(length = N.mc, mode = "list")
interv_QALY <- vector(length = N.mc, mode = "list")
CE_stats <- vector(length = n.scenarios, mode = "list")


pop_year <-  1000 ##TODO: get real value
```


Extract TB cases only data

```{r}
costeff_data <-
  cohort %>%
  select(cfr,
         QALY_statusquo,
         QALY_diseasefree,
         QALY_cured,
         QALY_fatality,
         uk_notif_discounts,
         all_notif_discounts,
         uk_secondary_inf_discounts,
         all_secondary_inf_discounts) %>%
  stats::na.omit()
```


We also calculate the expected statistics for reproducability and comparison with the randomly generated values.

```{r}

mean_cost.aTB_TxDx <- means_distributions(unit_cost$aTB_TxDx) %>% sum()
mean_num_sec_inf <- means_distributions(NUM_SECONDARY_INF) %>% unlist()

expected_costeff <-
  costeff_data %>% 
  transmute(cost_secondary_inf = mean_num_sec_inf * mean_cost.aTB_TxDx * all_secondary_inf_discounts,
            cost_notif.statusquo = (all_notif_discounts * mean_cost.aTB_TxDx) + cost_secondary_inf,
            QALY_notif.statusquo = (cfr * QALY_fatality) + ((1 - cfr) * QALY_cured))
```


## Main calculation

We iterate over all scenarios and all Monte-Carlo samples.
The `scenario_cost` and `scenario_QALY` functions calculate the values for each.
We then transpose the returned values from these functions and calculate the final statistics.

```{r}
for (s in seq_len(n.scenarios)) {

  set.seed(12345)

  for (i in seq_len(N.mc)) {
    
    interv_cost[[i]] <- scenario_cost(interv,
                                      unit_cost,
                                      NUM_SECONDARY_INF,
                                      costeff_data$uk_secondary_inf_discounts,
                                      num_all_tb_QALY = n_all_tb,
                                      costeff_data$uk_notif_discounts,
                                      n.diseasefree.all_tb[[s]][i],
                                      n.diseasefree.uk_tb[[s]][i])
    
    interv_QALY[[i]] <- scenario_QALY(avoided = n.diseasefree.all_tb[[s]][i],
                                      total = n_all_tb,
                                      costeff_data$QALY_statusquo,
                                      costeff_data$QALY_diseasefree)
  }
  
  CE_stats[[s]] <- costeff_stats(scenario_res[[s]],
                                 interv_QALY,
                                 interv_cost,
                                 costeff_data,
                                 expected_costeff)
}


#transpose CE_stats?

aTB_CE_stats <- list(QALY.statusquo = map(interv_QALY_vs, "statusquo"),
                     cost.statusquo = map(interv_cost_vs, "statusquo"),
                     QALY.screened = map(interv_QALY_vs, "screened"),
                     cost.screened = map(interv_cost_vs, "screened"),
                     QALY.screened_person = QALY.screened_person,
                     QALY.statusquo_person = QALY.statusquo_person,
                     cost.screened_person = cost.screened_person,
                     cost.statusquo_person = cost.statusquo_person,
                     cost_incur = cost_incur,
                     QALYgain = QALYgain,
                     cost_incur_person = cost_incur_person,
                     QALYgain_person = QALYgain_person,
                     E_cost_incur = E_cost_incur,
                     E_cost_incur_person = E_cost_incur_person,
                     E_QALYgain = E_QALYgain,
                     E_QALYgain_person = E_QALYgain_person,
                     pop_year = pop_year)

save(aTB_CE_stats,
     file = "aTB_CE_stats.RData")
```



```{r}

#' costeff_stats
#'
#' @param scenario_res 
#' @param interv_QALY
#' @param interv_cost
#' @param costeff_data 
#' @param expected_costeff
#' @param pop_year
#'
#' @return
#' @export
#'
#' @examples

costeff_stats <- function(scenario_res,
                          interv_QALY,
                          interv_cost,
                          costeff_data,
                          expected_costeff,
                          pop_year) {
  
  interv_cost_vs <-
    interv_cost %>%
    purrr::transpose() %>%
    simplify_all()
  
  interv_QALY_vs <-
    interv_QALY %>%
    purrr::transpose() %>%
    simplify_all()
  
  return(list(
    interv_cost_vs = interv_cost_vs,
    interv_QALY_vs = interv_QALY_vs,
    E_QALY_notif.screened = sum(scenario_res$p_LTBI_to_effectiveTx * costeff_data$QALY_diseasefree +
                                  (1 - scenario_res$p_LTBI_to_effectiveTx) * expected_costeff$QALY_notif.statusquo),
    
    E_cost_notif.screened = (1 - scenario_res$p_LTBI_to_effectiveTx) * sum(expected_costeff$cost_notif.statusquo),
    
    QALY.screened_person = interv_QALY_vs$screened/pop_year,
    QALY.statusquo_person = interv_QALY_vs$statusquo/pop_year,
    
    QALYgain = interv_QALY_vs$screened - interv_QALY_vs$statusquo,
    
    QALYgain_person = QALYgain/pop_year,
    
    cost.screened_person = interv_cost_vs$screened/pop_year,
    cost.statusquo_person = interv_cost_vs$statusquo/pop_year,
    
    cost_incur = interv_cost_vs$screened - interv_cost_vs$statusquo,
    cost_incur_person = cost_incur/pop_year,
    
    E_cost_incur = E_cost_notif.screened - sum(expected_costeff$cost_notif.statusquo),
    E_cost_incur_person = E_cost_incur/pop_year,
    
    E_QALYgain = E_QALY_notif.screened - sum(expected_costeff$QALY_notif.statusquo),
    E_QALYgain_person = E_QALYgain/pop_year))
}

```


