---
title: "Progression rate analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, warning=FALSE}
library(dplyr)
library(magrittr)
```

Construct the time to active TB as a mixture model with 2 components.

$$
p(\text{infected}) \times p(\text{infected at T=t | infected}).
$$
The conditional probability $p(\text{infected at T=t | infected})$ is produced from Sutherland () and extrapolating assuming an exponential decay to 1 in lifetime.
The marginal probability $p(\text{infected})$ is the chance of being infected in a lifetime.

The reason to do it like this is so that we can easily see the value of $p(\text{infected})$ for different estimates found in literature, without modifying $p(\text{infected at T=t | infected})$.

From Pareek (2011), they chose a conservative rate for LTBI to active TB of 5% over 20 years.
Marks et al (2000) calculated a progression rate of 6.7% over 40 years.
Choudhury (2013) estimated 13% over 10 years or 16.3% over 15 years.
2006 NICE economic appraisal said LTBI testing is cost-effective over 18% chance over 15 years and 2001 NICE economic appraisal reduced this to 12%.

```{r}
load(file = "../ext-data/year_prob.activetb_cens_exituk.RData")

year_prob.activetb_cens_exituk %>% cumsum %>% divide_by(max(.)) %>% plot(type = 'l')
```

```{r}
LIFETIME_RISK <- 0.163  #Choudhury (2013) 15 years
LIFETIME_RISK <- 0.18   #2006 NICE economic appraisal
LIFETIME_RISK <- 0.067  #Marks (2000) 40 years
```


