---
title: "A scenario decision tree simulation"
author: "Nathan Green"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
bibliography: active_tb_imputation.bib
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

 This document demonstrates running the screening, diagnosis and treatment decision tree model.
 

```{r, warning=F, message=F}
library(treeSimR)
library(LTBIscreeningproject)
library(dplyr)
library(data.tree)
library(purrr)
```


Load in data

```{r}
data("intervention_constants", package = "LTBIscreeningproject")
data("cost_effectivness_params", package = "LTBIscreeningproject")
data("scenario_parameters", package = "LTBIscreeningproject")
data("year_prob.activetb_cens_exituk", package = "LTBIscreeningproject")
data("year_prob.activetb_cmprsk_exituk", package = "LTBIscreeningproject")
data("model_input_cohort", package = "LTBIscreeningproject")
```


## Specific intervention data prep


According to the parameter values we specified in `interv` we first need to prepare the cohort data set.

Only use a single year cohort
```r
IMPUTED_sample_year_cohort <- dplyr::filter(IMPUTED_sample,
                                            issdt_year == interv$year_cohort)
```

EWNI stay long enough
```r
IMPUTED_sample_year_cohort <- dplyr::filter(IMPUTED_sample_year_cohort,
                                            date_exit_uk1_issdt.years >= interv$min_screen_length_of_stay)
```

Only keep those inidiviuals that are screened before some other event
```r
if (interv$screen_with_delay) {
  IMPUTED_sample_year_cohort <- dplyr::filter(IMPUTED_sample_year_cohort,
                                              screen == 1)}
```

Do we include student in the screening programme?
```r
if (interv$no_students) {
  IMPUTED_sample_year_cohort <- dplyr::filter(IMPUTED_sample_year_cohort,
                                              visatype2 != "Students")}
```

Remove individuals from 'lower' incidence countries
```r
IMPUTED_sample_year_cohort <- dplyr::filter(IMPUTED_sample_year_cohort,
                                            who_prev_cat_Pareek2011 %in% interv$incidence_grps_screen)
```

Count numbers of TB cases

```r
n.exit_tb <-
  IMPUTED_sample_year_cohort %>%
  dplyr::filter(exituk_tb) %>%
  dplyr::count()

n.uk_tb <-
  IMPUTED_sample_year_cohort %>%
  dplyr::filter(uk_tb) %>%
  dplyr::count()


num_all_tb_cost <-
  if (interv$ENDPOINT_cost == "exit uk") {
    n.uk_tb
  } else if (interv$ENDPOINT_cost == "death") {
    n.uk_tb + n.exit_tb}

num_all_tb_QALY <-
  if (interv$ENDPOINT_QALY == "exit uk") {
    n.uk_tb
  } else if (interv$ENDPOINT_QALY == "death") {
    n.uk_tb + n.exit_tb}
```


## Prep decision tree

Load input files. We have defined the decision tree using YAML syntax.
We have a separate trees for cost and health. They have the same structure and probabilities but different values on the branches. We also create our own class.

```r
osNode.cost.fileName <- system.file("data", "LTBI_dtree-cost-symptoms.yaml",
                                    package = "LTBIscreeningproject")

osNode.health.fileName <- system.file("data", "LTBI_dtree-QALYloss-symptoms.yaml",
                                      package = "LTBIscreeningproject")

costeff.cost <- treeSimR::costeffectiveness_tree(yaml_tree = osNode.cost.fileName)
osNode.cost <- costeff.cost$osNode

costeff.health <- treeSimR::costeffectiveness_tree(yaml_tree = osNode.health.fileName)
osNode.health <- costeff.health$osNode
```

```{r echo=F, out.width=20}
costeff.cost <- treeSimR::costeffectiveness_tree(yaml_tree = "LTBI_dtree-cost-symptoms.yaml")
print(costeff.cost)
```


Create look-up tables using the cohort data to give proportion in each incidence in country of origin and the probability of LTBI for each of these.

```r
who_levels <- c("(0,50]", "(50,150]", "(150,250]", "(250,350]", "(350,1e+05]")

p_incid_grp <- miscUtilities::prop_table(IMPUTED_sample_year_cohort$who_prev_cat_Pareek2011)

pLatentTB.who <- data.frame(who_prev_cat_Pareek2011 = names(p_incid_grp),
                            LTBI = c(0.03, 0.13, 0.2, 0.3, 0.3))
```

Then insert these probabilities in to the decision tree
```r
for (i in seq_along(who_levels)) {

  osNode.cost$Set(p = p_incid_grp[i],
                  filterFun = function(x) x$name == who_levels[i])

  osNode.health$Set(p = p_incid_grp[i],
                    filterFun = function(x) x$name == who_levels[i])
}

for (i in who_levels) {

  pLTBI <- subset(pLatentTB.who,
                  who_prev_cat_Pareek2011 == i,
                  select = LTBI)

  osNode.cost$Set(p = pLTBI,
                  filterFun = function(x) x$pathString == miscUtilities::pastef("LTBI screening cost", i, "LTBI"))
  osNode.health$Set(p = pLTBI,
                    filterFun = function(x) x$pathString == miscUtilities::pastef("LTBI screening QALY loss", i, "LTBI"))

  osNode.cost$Set(p = 1 - pLTBI,
                  filterFun = function(x) x$pathString == miscUtilities::pastef("LTBI screening cost", i, "non-LTBI"))
  osNode.health$Set(p = 1 - pLTBI,
                    filterFun = function(x) x$pathString == miscUtilities::pastef("LTBI screening QALY loss", i, "non-LTBI"))
}
```

## Decision tree output


```{r}
decision_tree_cluster(parameters = scenario_parameters[[1]],
                       n.uk_tb = 10,
                       n.exit_tb = 10,
                       cost_dectree = "osNode_cost_2009.Rds",
                       health_dectree = "osNode_cost_2009.Rds")
```
